Certified Symbolic Transducer with the Application of String Solver

### 2025-02-28 Paper/main.tex
remove old tests

For a word $w = a_0,\ldots, a_{n-1}$, it is accepted by $\sigma$ iff $a_i \in \llbracket\psi_i \rrbracket$ for $0 \leq i \leq n - 1$. Run $\sigma$ will generate an output sequence if $w$ is accepted by it, which is $w'= (f_0~a_0), \ldots (f_{n_1}~a_{n_1})$. We call in the sequent:
\begin{itemize}
\item  $(a_0,(f_0~a_0)), \ldots, (a_{n-1},(f_{n-1}~a_{n-1}))$ a \emph{path},
\item $a_0,\ldots,a_{n-1}$ the \emph{input} of the path and $(f_0~a_0), \ldots, (f_{n-1}~a_{n-1})$ the \emph{output} of the path.
\end{itemize}

If $a_0,\ldots,a_{n-1}$ is accepted by an accepting run in $\mathcal{T}$, we say that the path is an accepting path of $\mathcal{T}$.
For a path $\pi$, we denote the input of $\pi$ as $in(\pi)$ and the output of $\pi$ as $out(\pi)$.
%
Given an SFT $\mathcal{T}$ and a word $w$, we define the operation product of $\mathcal{T}$ and $w$ (denoted as $\mathcal{T}\times\{w\}$) as the set of outputs generated by $\mathcal{T}$ with the input $w$. More precisely, 
\[
\mathcal{T}\times\{w\} = \{w'\mid \exists \pi.~\pi \text{ is an accepting path }\land in(\pi) = w \land out(\pi) = w'\}.
\]

>>>>

For a word $w = a_0,\ldots, a_{n-1}$, it is accepted by $\sigma$ iff $a_i \in \llbracket\psi_i \rrbracket$ for $0 \leq i \leq n - 1$. Run $\sigma$ will generate an output sequence if $w$ is accepted by it, which is $w'= (f_0~a_0), \ldots (f_{n_1}~a_{n_1})$. We call in the sequent:
\begin{itemize}
\item  $(a_0,(f_0~a_0)), \ldots, (a_{n-1},(f_{n-1}~a_{n-1}))$ a \emph{trace},
\item $a_0,\ldots,a_{n-1}$ the \emph{input} of the trace and $(f_0~a_0), \ldots, (f_{n-1}~a_{n-1})$ the \emph{output} of the trace.
\end{itemize}

If $a_0,\ldots,a_{n-1}$ is accepted by an accepting run in $\mathcal{T}$, we say that the trace is an accepting trace of $\mathcal{T}$.
For a trace $\pi$, we denote the input of $\pi$ as $in(\pi)$ and the output of $\pi$ as $out(\pi)$.
%
Given an SFT $\mathcal{T}$ and a word $w$, we define the operation product of $\mathcal{T}$ and $w$ (denoted as $\mathcal{T}\times\{w\}$) as the set of outputs generated by $\mathcal{T}$ with the input $w$. More precisely, 
\[
\mathcal{T}\times\{w\} = \{w'\mid \exists \pi.~\pi \text{ is an accepting trace }\land in(\pi) = w \land out(\pi) = w'\}.
\]
